---
title: "README"
author: "Bob Rudis"
date: "`r Sys.Date()`"
output:
  md_document:
    variant: markdown_github
---
[![Build Status](https://travis-ci.org/hrbrmstr/Rforecastio.svg)](https://travis-ci.org/hrbrmstr/Rforecastio) 

Rforecastio - API access to the [Forecast API](https://developer.forecast.io/docs/v2) from R.

- Forecast API Docs: https://developer.forecast.io/docs/v2
- Forecast Dev site: https://developer.forecast.io/

**NOTE: THIS IS A MAJOR REWRITE OF THE INTERFACE**

One of the biggest changes (besides splitting one function into two) is that the
API wrapper functions in this package all rely on a ForecastIO API
key that now resides in the environment variable \code{FORECASTIO_API_KEY}. The
easiest way to get this into your environment is to set it in the `\code{.Renviron}` file in your
home directory.

The following functions are implemented:

- `forecastio_api_key` :	Get or set FORECASTIO_API_KEY value
- `get_current_forecast` : Retrieve the current forecast (for the next week)
- `get_forecast_for` : Retrieve weather data for a specific place/time
- `plot.rforecastio` : Plot method for rforecastio objects

There have been several major enhancements to the way this package works with the API. Also,
the structures returned in the list are now classes as `rforecastio` objects (which afford the 
use of an S3 plotting method) and the data frames are now `tbl_df` objects (so they work like
regular data frames but get all the `dplyr` goodness, too).

### News

- Version 2.0.0 released - complete overhaul of the package
- Version 2.0.1 released - Did a check `--as-cran` and fixed _many_ things invisible to the users of this package

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/Rforecastio")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(Rforecastio)

# current verison
packageVersion("Rforecastio")

now <- get_current_forecast(43.2672, -70.8617)
print(now$hourly)

then <- get_forecast_for(43.2672, -70.8617, "2013-05-06T12:00:00-0400")
print(then$daily)

print(sprintf("You have used %s API calls.", then$`x-forecast-api-calls`))

plot(now)
```

### Test Results

```{r}
library(Rforecastio)
library(testthat)

date()

test_dir("tests/")
```

