---
output: rmarkdown::github_document
---
[![Build Status](https://travis-ci.org/hrbrmstr/Rforecastio.svg)](https://travis-ci.org/hrbrmstr/Rforecastio) 

`Rforecastio` : Tools to Work with the Dark Sky API

- Forecast API Docs: https://darksky.net/dev/docs
- Forecast Dev site: https://darksky.net/dev/

The following functions are implemented:

- `forecastio_api_key` :	Get or set FORECASTIO_API_KEY value
- `get_current_forecast` : Retrieve the current forecast (for the next week)
- `get_forecast_for` : Retrieve weather data for a specific place/time
- `plot.rforecastio` : Plot method for rforecastio objects
- `print.rforecastio` : A tad more human readable default printing

There have been several major enhancements to the way this package works with the API. Also,
the structures returned in the list are now classes as `rforecastio` objects (which afford the 
use of an S3 plotting method) and the data frames are now `tbl_df` objects (so they work like
regular data frames but get all the `dplyr` goodness, too).

### News

- 2.3.0 - Fixed API URL (thx Lasse Vilhelmsen!)
- 2.2.0 - `print()` method, made JSON & headers optional in respons object, smarter printing
- Version 2.1.1 released - fix "language" parameter per #9
- Version 2.1.0 released - added `httr::GET` pass-through `...` parameter to salient functions
- Version 2.0.0 released - complete overhaul of the package
- Version 2.0.1 released - Did a check `--as-cran` and fixed _many_ things invisible to the users of this package

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/Rforecastio")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(Rforecastio)

# current verison
packageVersion("Rforecastio")

now <- get_current_forecast(43.2672, -70.8617)
print(now)

then <- get_forecast_for(43.2672, -70.8617, "2013-05-06T12:00:00-0400", add_headers=TRUE)
print(then)

# getting data for more than one location

more_than_one <- data.frame(loc=c("Maine", "Seattle"),
                            lon=c(43.2672, 47.6097),
                            lat=c(70.8617, 122.3331),
                            when=c("2013-05-06T12:00:00-0400",
                                   "2013-05-06T12:00:00-0400"),
                            stringsAsFactors=FALSE)

bigger_list <- mapply(get_forecast_for, 
       more_than_one$lon, more_than_one$lat, more_than_one$when,
       SIMPLIFY=FALSE)
names(bigger_list) <- more_than_one$loc

bigger_list$Seattle[[1]]

bigger_list$Maine[[1]]

print(sprintf("You have used %s API calls.", then$`x-forecast-api-calls`))

plot(now)
```

### Test Results

```{r}
library(Rforecastio)
library(testthat)

date()

test_dir("tests/")
```

